HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-04 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex

	\item {\em ``It is written that represents the index of fashion trends, but it is unclear what exactly it refers to. Does it correspond to a product/item?''} \medskip

	\textbf{Author response:} We understand this remark and further information has been added in the revised paper to clarify this point. The index of fashion trends represents the name of a fashion clothing relevant for the fashion industry. It can be just one attribute detected by a visual recognition model (ex: the sneakers) but it can also be a combination of several attributes (ex: the A-line dress). As the fashion trends names are anonymized in the proposed dataset, the architecture behind the fashion trends definition is not presented in this paper.\\

	\item {\em ``I didn't know what statistic was $\hat{y}^{c,g,m}$. Could you please explain it in detail?''} \medskip

	\textbf{Author response:} We are not sure of the notation in the question of the referee, in the paper we introduce $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ but not $\hat{y}^{c,g,m}$. We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$:
	\begin{itemize}
	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$. It can be for example the time series representing the evolution of the general pants for females in Europe. The sequence $\Tilde{y}^{c,g,m}$ is then used to normalize each time series $y^{c,g,m,i}$ with the same $c$, $g$ and $m$. All the fashion trends of pants for females in Europe are normalized by the time series representing the general pants for females in Europe.
	\item $\bar{y}^{c,g,m}$ is the time series $\Tilde{y}^{c,g,m}$ where the seasonality component has been removed. The seasonality component is removed as we only want to remove social media bias with the normalization step and not remove or change the seasonality of the proposed fashion trends.
	\end{itemize}	
To remove all gray area on this topic, additional information (regarding the Jersey Top normalization example) has been added at the end of Section 2.2 and in the legend to Figure 3.

@@

	\item {\em ``It would be good to add a discussion of the limitations of this study. Other external factors could be various, such as advertisements. This study focuses on the correlation between weak signals and trends, not causality. This should be clearly stated. As seen in Figure 2, the effect of the external factor is accompanied by a time delay. It would be interesting to analyze how such time delays vary by fashion category and market. It would also be interesting to incorporate this into machine learning models.''} \medskip

	\textbf{Author response:} We thank the referee for this remark and supplementary information has been added in the result sections and in the appendix of the revised paper. As future works on the dataset, we attempt to build a second fashion dataset gathering more time series and additional external signals such as fashion shows signals, brands signals etc...
Concerning the forecasting model, we acknowledge that we did not discuss enough about the limits of the proposed approach. In the revised version of the paper, a discussion section is added at the end of Section 4. For instance, we agree that designing models to explain the time delay between weak signals shifts and their consequences on the target signals is an interesting objective. We believe that this is out of the scope of the present paper but this is the topic of an ongoing work using hidden states to leverage  the impact of external signals on the main signal.\\

### 2023-07-05 tmlr_submission/hermes_paper_revision/hermes_paper.tex
minor changes

where T denotes the number of available time steps \textcolor{orange}{and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$}. The time series $y^{c,g,m,\textcolor{orange}{j}}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. \textcolor{orange}{In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top,  $g$=Female, $m$=China and  $j$=Jersey top) are presented. So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China.}

>>>>

where T denotes the number of available time steps \textcolor{orange}{and $i$ represent a unique identifier summarizing the 4 information $c$, $g$, $m$ and $j$}. The time series $y^{c,g,m,\textcolor{orange}{j}}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. \textcolor{orange}{In this example, the raw and normalized time series of the Jersey top trend for females in China ($y^{c,g,m,j}$ with $c$=Top, $g$=Female, $m$=China and $j$=Jersey top) are presented. So as to compute the normalized signal, the raw time series of the Jersey top trend for females in China is divied by the deseasonalized raw time series representing the global Top trend for female in China ($\bar{y}^{c,g,m}$ with $c$=Top, $g$=Female and $m$=China).}
